\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath} \usepackage{amssymb} \usepackage{url} \textheight=10in
\usepackage{hyperref}
\pagestyle{empty}
% \raggedbottom
\raggedright

% \renewcommand{\encodingdefault}{cg}
% \renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME
\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1} #2 \end{verse}
} \newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt}
    \textsc{#1}} \vspace*{-6pt} \lineunder} \newcommand{\employer}[3]{{
    \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\ }}
\newcommand{\contact}[3]{
  \vspace*{-8pt}
  \begin{center}
    {\LARGE \scshape {#1}}\\ #2 \lineunder #3
  \end{center}
  \vspace*{-8pt} }
\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep
      -2pt}}{\vspace*{4pt}\end{list}} \newcommand{\schoolwithcourses}[4]{
  \textbf{#1} #2 \\ #3\\ #4 \\
  \vspace*{5pt} } \newcommand{\school}[4]{ \textbf{#1} #2 $\bullet$ #3\\ #4
  \\ }
% END RESUME DEFINITIONS

\begin{document}

\small
\smallskip
\vspace*{-44pt}

\contact{Juan Pemberthy} { Boston, Massachusetts +1 415-535-9740}
        { $\bullet$ juan@pemberthy.com $\bullet$
          juan.pemberthy.com
        }

\header{Work History}

\employer{GitHub - Boston, MA}{January 2019 - Present}{Senior Software Engineer}
\begin{achievements}
\item Contributed to the ecosystem-apps team, focusing on programmatic access technologies including GitHub Apps, OAuth Apps, and Personal Access Tokens.
\item Designed and developed Global Apps, a scalable solution that powers GitHub's globally available products like GitHub Actions, Copilot, Dependabot, and Codespaces.
\item Spearheaded the design and implementation of robust observability, monitoring, and availability tooling for programmatic access.
\item Successfully restructured the API authorization logic to improve maintainability of this layer, which serves billions of daily requests.
\item Implemented and released the second generation of Personal Access Tokens, enhancing security and usability.
\end{achievements}

\employer{Uber Technologies - San Francisco, CA}{November 2014 - January 2019}{Senior Software Engineer II}
\begin{achievements}
\item Developed and maintained the first-generation systems for Uber's External API, including the OAuth2.0 provider, API backend, sandbox, and webhooks service.
\item Designed and developed the second generation of Uber's External API platform.
\item Created a high-level testing tool to ensure API endpoint consistency across various environments, including production and sandbox.
\item Designed, developed and owned the backend system powering positioning suggestions for Uber drivers.
\item Contributed to the backend development of the Uber driver app, focusing on suggestions and estimated time of requests.
\end{achievements}

\employer{We Heart It - San Francisco, CA}{May 2012 - November 2014}{Senior Software Engineer}
\begin{achievements}
\item Designed and developed the internal API that supports both the iOS and Android mobile applications.
\item Developed and scaled systems to distribute millions of "hearts" (likes) across thousands of user dashboards.
\item Created the image upload service to streamline media management.
\item Used a diverse set of tools for service development, including Ruby, Ruby on Rails, MySQL, Redis, Lua, Cassandra, Node.js, and RabbitMQ.
\end{achievements}

\employer{Stack Builders Inc - Remote}{November 2010 - March 2012}{Software Engineer}
\begin{achievements}
\item Developed a geolocation-based micro-messaging social network as well as private applications tailored for the financial leaders sector. The primary technologies used in building these services were Ruby on Rails, MySQL, and MongoDB.
\end{achievements}

\employer{Eureka Facts LLC - Rockville, MD}{2009}{Software Engineer Intern}
\begin{achievements}
\item Conducted survey programming, online data capture, web development and business intelligence tool customization.
\end{achievements}

\header{Open Source, Personal Projects and Publications}
\begin{achievements}
\item \href{https://web.tecgraf.puc-rio.br/~abraposo/pubs/SVR2008/SVR2008_full_proceedings.pdf}{Telepresence: A tool for distance education} Pemberthy et al. 2008 – X Symposium on Virtual and Augmented Reality.
\item \url{https://github.com/jpemberthy/} for all my open source projects.
\item \url{http://timehub.me/} - Invoicing for GitHub. Winner of the 2011 Rally on Rails.
\item \url{http://bolsaenred.com/} - A Community for people investing in the Colombian Stock Exchange.
\item \url{https://github.com/jpemberthy/uber-activity} -A sinatra application that makes use of the Uber API to show your recent rides info and stats.
\item \url{https://github.com/jpemberthy/ezgraphix} - A Rails plugin to generate chart graphics.
\end{achievements}

\header{Education}

\schoolwithcourses{Universidad EAFIT (Medell\'in, Colombia)}{}
{2010 Bachelor in Computer Science}
{Current Cumulative (GPA): 4.23/5}
\smallskip
\vspace*{10pt}

\end{document}
